%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dokument-Einstellungen
\documentclass{SMBV12}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------
% Hier beginnt das eigentliche Dokument
\begin{document}

\title{Graph-Based Segmentation}

\author{Phan-Anh Nguyen}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------% Zusammenfassung

\begin{abstract}%
Abstract. This 20-page seminar paper reviews the state-of-the-art graph-based segmentation algorithms.
\end{abstract}

\keywords{Classification, Graph Cut, Segmentation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------
%
\section{Introduction}

Introduction is written at last.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------
%
\section{Image Features}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Image Feature Overview}

What are image features? How can we describe/represent them?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SURF descriptor}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Edges and Contours}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}

pros and cons. Which descriptor is suitable for a particular case.

\section{Supervised versus Unsupervised Methods}



\subsection{Supervised Methods}



\subsubsection{Bag of Visual Words}



\subsubsection{Support Vector Machine}



\subsubsection{Statistical Shape Model}



\subsection{Unsupervised Methods}



\section{Graph Construction}

Intuitive connection between graphs and images.

\subsection{Region Graph}

Graph of small over-segmented regions.

\subsection{Contour Graph}

\subsection{Markov Random Field}

\section{Cut Problem Formulation}

\subsection{Prize-collecting Steiner Tree}

\subsection{Hermitian Eigenvalue Problem}

\subsection{Multi-Shape Graph-Cut}

\section{Typical Applications}

\subsection{Efficient Region Search for Object Detection}

\subsection{Multi-Shape Graph-Cut for Lung Segmentation}

\subsection{Salient Contour Detection}

\section{Conclusion}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-----------------------------------------------------------
%
\def\refname{Literature}
\begin{thebibliography}{AA}



\end{thebibliography}

\newpage
\noindent
\begin{picture}(160,242)
\put(0,0){\framebox(160,242){}}
\end{picture}

\end{document}
